Rapid Cycleway Prioritisation Tool

### 2020-06-12 report.Rmd
Typo fix II
grouping methods

The rationale was to provide interactive evidence that supports scheme prioritisation based on a range of variables.
Length, for example, is important for creating a joined-up and continuous, a vital component of cycling strategies [@parkin_designing_2018].

@@

Only roads with a continuous length above a threshold distance (500 m) identified as candidates for inclusion in the Top ranked new cycleways layer. 
Roads with an existing cycleway along 75% or more of their length were excluded (we selected such a high value because the presence of a cycleway in OSM does not guarantee that this is a high quality, continuous route).
Roads were ranked in terms of their cycling potential and highest ranking roads were included in the roads.
The number of roads identified as Top ranked new cycleways varies depending on the size of the authority, ranging from 4 in the [Isle of Wight](https://www.cyipt.bike/rapid/isle-of-wight/) to 80 in [Greater London](https://www.cyipt.bike/rapid/greater-london/).

>>>>

The rational was to provide interactive evidence that supports scheme prioritisation based on a range of variables.
Length, for example, is important for creating a joined-up and continuous network, a vital component of cycling strategies [@parkin_designing_2018].

@@

Only roads with a continuous length above a threshold distance (500 m) identified as candidates for inclusion in the Top ranked new cycleways layer. 
Roads with an existing cycleway along 80% or more of their length were excluded (we selected such a high value because the presence of a cycleway in OSM does not guarantee that this is a high quality, continuous route).
Roads were ranked in terms of their cycling potential and highest ranking roads were included in the roads.
The number of roads identified as Top ranked new cycleways varies depending on the size of the authority, ranging from 4 in the [Isle of Wight](https://www.cyipt.bike/rapid/isle-of-wight/) to 80 in [Greater London](https://www.cyipt.bike/rapid/greater-london/).
